Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
State that evidence should be testable
Revert "terminology: example, expectation, property"
This reverts commit 6f683578e639582483c96cd5c53471d261983c33.

We use /code example/ and /interactive example in the text.  So I think
it is a good idea to keep them in the terminology.

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.  Most existing BDD tools use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec, supports
both code examples and \emph{properties} as evidence.
It can verify examples and test properties, and it can create an
informal specification document from that.

@@

\item[example]
    An example is a piece of source code that shows how a function is
    used.  It consists of the function call with concrete values as
    parameters, together with the expected outcome.  The outcome can
    be given as a pure value, or in the case of impure code, as a
    short GHCi session.

\item[expectation]
    An expectation is a proposition that defines the anticipated
    outcome of a function call.  Expectations serve the same purpose
    as \emph{assertions} in classical unit testing frameworks, but use
    a different terminology. For instance, instead of
    \begin{quote}
    \small
    \begin{verbatim}assertEqual (gcd 13 7) 1\end{verbatim}
    \end{quote}
    we write
    \begin{quote}
    \small
    \begin{verbatim}gcd 13 7 `shouldBe` 1\end{verbatim}
    \end{quote}

\item[property]
    A property is a piece of code similar to an example, except that
    some parameters of the function call are abstracted from.  The
    test framework runs a property several times with different
    parameters, resulting in several outcomes. The expectation is
    therefore not given as a concrete value, but as a predicate which
    all outcomes should satisfy.

@@

\item[evidence]
    Evidence provides some confidence that a function exhibits a
    certain behavior.  In Haskell we use examples and properties as
    evidence.

>>>>

In BDD, all behavior should be documented, together with some testable
\emph{evidence} for that behavior.  Most existing BDD tools use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec, supports
both code examples and \emph{properties} as evidence.
It can verify examples and test properties, and it can create an
informal specification document from that.

@@

\item[example]
    An example shows how a function is used.  It is either a \emph{code
    example} in the form of an HUnit test case; or an \emph{interactive
    example}, given as a short GHCi session.

\item[expectation]
    Expectations are used to define the expected outcome of a code
    example.  They serve the same purpose as \emph{assertions} in xUnit
    testing frameworks, but use a different terminology.

\item[property]
    Property means a QuickCheck property as defined in
    \cite{quickcheck}.

@@

\item[evidence]
    Evidence provides some confidence, that a function exhibits a
    certain behavior.  In Haskell we use examples and properties as
    evidence.
